Supplementary Information

### 2021-06-10 doc/manuscript/ForestGEO_treerings.Rmd
experimenting with proposed restructuring of intro
@srusso2 , FYI. I don't think this works as well and plan to revert this commit and make smaller changes, keeping the original structure.

To realistically estimate forest woody productivity, it is necessary to measure or model the growth rate of individual trees within a stand based on the primary biotic and abiotic drivers.
Specifically, what is needed is an analysis framework that can capture the additive and interactive effects of climate, tree size (most commonly diameter at breast height, DBH), and other environmental drivers, all of which may be best described by nonlinear functions [@muller-landau_testing_2006; @rollinson_climate_2021].
While multifactorial and sometimes non-linear individual-based analysis frameworks have been applied in tree-ring analysis [e.g., @evans_fusing_2017; @klesse_amplifying_2020; @zuidema_recent_2020; @rollinson_climate_2021], their use has been relatively limited, and none simultaneously account for climate, DBH, and calendar year (a proxy for slowly changing environmental drivers).
In the following paragraphs, we outline major hypotheses regarding the influence of these factors on tree growth that can best be addressed using a multifactorial, non-linear approach to tree-ring analysis (Table `r hypotheses`).

@@

Here, we develop and apply a new method that allows simultaneous consideration of the effects of primary climate drivers (i.e., the most influential climate variables and the seasonal window over which they operate), DBH, and calendar year on annual tree growth.
This approach allows us to address the above hypotheses concerning the primary drivers of individual tree growth (Table `r hypotheses`) across ten forested sites spanning 52 degrees latitude.

>>>>

To realistically estimate forest woody productivity, it is necessary to measure or model the growth rate of individual trees within a stand based on the primary biotic and abiotic drivers.
Specifically, what is needed is an analysis framework that can capture the additive and interactive effects of climate, tree size (most commonly diameter at breast height, DBH), and other environmental drivers, all of which may be best described by nonlinear functions [@muller-landau_testing_2006; @rollinson_climate_2021].
While multifactorial and sometimes non-linear individual-based analysis frameworks have been applied in tree-ring analysis [e.g., @evans_fusing_2017; @klesse_amplifying_2020; @zuidema_recent_2020; @rollinson_climate_2021], their use has been relatively limited, and none simultaneously account for climate, DBH, and calendar year (a proxy for slowly changing environmental drivers).
In the following paragraphs, we outline major hypotheses regarding the influence of these factors on tree growth that can best be addressed using a multifactorial, non-linear approach to tree-ring analysis (Table `r hypotheses`).
We then develop and apply a new method that allows simultaneous estimation of the effects of these drivers on annual tree growth, and address these key hypotheses (Table `r hypotheses`) across ten forested sites spanning 52 degrees latitude.

```
## Key hypotheses on tree growth {-#Key}

@@
